---
title: "1D simulation study"
author: "Yuxiao Li"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: true
  html_document:
    toc: true
    number_sections: true
    code_folding: hide
---

# Overview
This is the code for generating 1D nonstationary Gaussian random field with nonstationary variance only. It includes 5 sections: "Libraries" to load the required library; "Functions" to write down the required functions for the estimation procedures; "Estimation", the main function, to generate Gaussian random field and estimate parameters; and "Results" to show the results including table and figures.

## Libraries

```{r load_libs}
library(geoR)
library(fda)
library(ggplot2)
library(cowplot)
library(stats4)
library(here)
```

## Functions
```{r 1d beta0 lik}
##likelihood function for estimating beta0
##Input:
##location: n by 2 matrix
##data: length n vector
##params: spatial varying parameters, sigma
##Output:
##Log likelihood
lik1<-function(params,location,data){
    sigmasq <- params^2
    n <- dim(location)[1]
    dist <- matrix(0,n,n)
    for (i in 1:n){
        for(j in 1:n){
            dist[i,j] <- sqrt(sum((location[i,]-location[j,])^2))  
        }
    }
  
    cov <- cov.spatial(dist, cov.model = "matern", 
                       cov.pars = c(sigmasq, 0.2), kappa = 1)
    Eigen <- eigen(cov)
    Eigen_value <- diag(Eigen$values)
    Eigen_vec <- Eigen$vectors
    Cov.inv <- Eigen_vec %*% diag(1/diag(Eigen_value)) %*% t(Eigen_vec)
    loglikelihood <- 2 * (sum(log(2*pi*diag(Eigen_value))) + 
                                     sum(diag(t(data) %*% Cov.inv %*% data)))
    if (abs(loglikelihood) == Inf) {
        loglikelihood <- 1e+05
    }
    return(loglikelihood)
}
```


```{r 1d beta1 lik}
##likelihood function for estimating beta1
##Input:
##location: n by 2 matrix
##data: length n vector
##beta0: intercept of sigma, estimated using function lik1
##beta1: slope of sigma
##Output:
##Log likelihood
lik2<-function(beta1, beta0, location, data){
    sigmasq <- (beta0 + beta1*(location[,1]-mean(location[,1])))^2
    n <- dim(location)[1]
    dist <- sigmamat <- matrix(0,n,n)
    for (i in 1:n){
        for(j in 1:n){
            dist[i,j] <-sqrt(sum((location[i,]-location[j,])^2))
            sigmamat[i,j] <-sqrt(sigmasq[i]*sigmasq[j])
        }
    }
    cov <- cov.spatial(dist, cov.model = "matern", 
                     cov.pars = c(1, 0.2), kappa = 1)
    Eigen <- eigen(sigmamat*cov)
    Eigen_value <- diag(Eigen$values)
    Eigen_vec <- Eigen$vectors
    Cov.inv <- Eigen_vec %*% diag(1/diag(Eigen_value)) %*% t(Eigen_vec)
    loglikelihood <- 2 * (sum(log(2*pi*diag(Eigen_value))) + 
                                     sum(diag(t(data) %*% Cov.inv %*% data)))
    if (abs(loglikelihood) == Inf) {
        loglikelihood <- 1e+05
    }
    return(loglikelihood)
}
```

```{r 1d two nonstationary parameters beta 0}
##likelihood function for estimating beta0
##Input:
##location: n by 2 matrix
##data: length n vector
##params: spatial varying parameters, sigma
##Output:
##Log likelihood
lik3<-function(params,location,data){
    sigmasq <- params[1]^2
    lambda <- params[2]
    n <- dim(location)[1]
    dist <- matrix(0,n,n)
    for (i in 1:n){
        for(j in 1:n){
            dist[i,j] <- sqrt(sum((location[i,]-location[j,])^2))  
        }
    }
  
    cov <- cov.spatial(dist, cov.model = "matern", 
                       cov.pars = c(sigmasq, lambda), kappa = 1)
    Eigen <- eigen(cov)
    Eigen_value <- diag(Eigen$values)
    Eigen_vec <- Eigen$vectors
    Cov.inv <- Eigen_vec %*% diag(1/diag(Eigen_value)) %*% t(Eigen_vec)
    loglikelihood <- 2 * (sum(log(2*pi*diag(Eigen_value))) + 
                                     sum(diag(t(data) %*% Cov.inv %*% data)))
    if (abs(loglikelihood) == Inf) {
        loglikelihood <- 1e+05
    }
    return(loglikelihood)
}
```

```{r 1d two nonstationary parameters beta 1}
##likelihood function for estimating beta1
##Input:
##location: n by 2 matrix
##data: length n vector
##beta0: intercept of sigma, estimated using function lik1
##beta1: slope of sigma
##Output:
##Log likelihood
lik4<-function(params, beta0,location, data){
    sigmasq <- (beta0[1] + params[1]*(location[,1]-mean(location[,1])))^2
    lambda <- beta0[2] + params[2]*(location[,1]-mean(location[,1]))
    n <- dim(location)[1]
    dist <- sigmamat <- matrix(0,n,n)
    for (i in 1:n){
        for(j in 1:n){
            dist[i,j] <-sqrt(sum((location[i,]-location[j,])^2))
            sigmamat[i,j] <-sqrt(sigmasq[i]*sigmasq[j])
        }
    }
    cov <- cov.spatial(dist, cov.model = "matern", 
                     cov.pars = c(1, lambda), kappa = 1)
    Eigen <- eigen(sigmamat*cov)
    Eigen_value <- diag(Eigen$values)
    Eigen_vec <- Eigen$vectors
    Cov.inv <- Eigen_vec %*% diag(1/diag(Eigen_value)) %*% t(Eigen_vec)
    loglikelihood <- 2 * (sum(log(2*pi*diag(Eigen_value))) + 
                                     sum(diag(t(data) %*% Cov.inv %*% data)))
    if (abs(loglikelihood) == Inf) {
        loglikelihood <- 1e+05
    }
    return(loglikelihood)
}
```

```{r 1d three nonstationary parameters beta 0}
##likelihood function for estimating beta0
##Input:
##location: n by 2 matrix
##data: length n vector
##params: spatial varying parameters, sigma
##Output:
##Log likelihood
lik5<-function(params,location,data){
    sigmasq <- params[1]^2
    lambda <- params[2]
    eta <- params[3]
    n <- dim(location)[1]
    dist <- matrix(0,n,n)
    for (i in 1:n){
        for(j in 1:n){
            dist[i,j] <- sqrt(sum((location[i,]-location[j,])^2))  
        }
    }
  
    cov <- cov.spatial(dist, cov.model = "matern", 
                       cov.pars = c(sigmasq, lambda), kappa = 1)
    cov <- cov + diag(rep(eta,n))
    Eigen <- eigen(cov)
    Eigen_value <- diag(Eigen$values)
    Eigen_vec <- Eigen$vectors
    Cov.inv <- Eigen_vec %*% diag(1/diag(Eigen_value)) %*% t(Eigen_vec)
    loglikelihood <- 2 * (sum(log(2*pi*diag(Eigen_value))) + 
                                     sum(diag(t(data) %*% Cov.inv %*% data)))
    if (abs(loglikelihood) == Inf) {
        loglikelihood <- 1e+05
    }
    return(loglikelihood)
}
```

```{r 1d three nonstationary parameters beta 1}
##likelihood function for estimating beta1
##Input:
##location: n by 2 matrix
##data: length n vector
##beta0: intercept of sigma, estimated using function lik1
##beta1: slope of sigma
##Output:
##Log likelihood
lik6<-function(params,beta0, location, data){
    sigmasq <- (beta0[1] + params[1]*(location[,1]-mean(location[,1])))^2
    lambda <- beta0[2] + params[2]*(location[,1]-mean(location[,1]))
    eta <- beta0[3] + params[3]*(location[,1]-mean(location[,1]))
    n <- dim(location)[1]
    dist <- sigmamat <- matrix(0,n,n)
    for (i in 1:n){
        for(j in 1:n){
            dist[i,j] <-sqrt(sum((location[i,]-location[j,])^2))
            sigmamat[i,j] <-sqrt(sigmasq[i]*sigmasq[j])
        }
    }
    cov <- cov.spatial(dist, cov.model = "matern", 
                     cov.pars = c(1, lambda), kappa = 1)
    cov <- cov + diag(eta)
    Eigen <- eigen(sigmamat*cov)
    Eigen_value <- diag(Eigen$values)
    Eigen_vec <- Eigen$vectors
    Cov.inv <- Eigen_vec %*% diag(1/diag(Eigen_value)) %*% t(Eigen_vec)
    loglikelihood <- 2 * (sum(log(2*pi*diag(Eigen_value))) + 
                                     sum(diag(t(data) %*% Cov.inv %*% data)))
    if (abs(loglikelihood) == Inf) {
        loglikelihood <- 1e+05
    }
    return(loglikelihood)
}
```


```{r function to compute CI}
CI.1d <- function(fit = NULL){
    fisher_info <- 1/fit$hessian
    prop_sigma <- sqrt(fisher_info)
    upper <- fit$par+1.96*prop_sigma
    lower <- fit$par-1.96*prop_sigma
    interval <- data.frame(value=fit$par, upper=upper, lower=lower)
    interval
}

```

```{r function to compute weight}
weight.fun <- function(h,N,k){
weight <- matrix(0,N,k)
mcloc <- (1:k)/k-1/(2*k)
t <- (1:N)/N
for(i in 1:N){
    for(k in 1:k){
        weight[i,k]<- exp(-(t[i] - mcloc[k])^2/2/h)
    }
    weight[i,] <- weight[i,]/sum(weight[i,])
}
weight
}
```


## Estimation

###Generate and plot simulated data
```{r generating data}
N <- 200
##parameter setup
t <- (1:N)/N
m <- 4
##true sigma
y <- (2 * sin(t/0.15) + 2.8)
v.vec <- v2.vec <- c()

##simulate Gaussian random field
set.seed(1)
sim11 <- grf(N, grid = "reg", ny = 1, 
             nsim = 1000, xlims = c(0,1),cov.model ="matern",
             cov.pars = c(1, 0.2), kappa = 1, nug = 0, mean = 0)
#image(sim11)
u_1 <- y * sim11$data[,2]


```

```{r plot realization}
plot1 <- qplot(t,u_1,geom = "line",xlab = 's',ylab = 'Z',main='(a)')
plot2 <- qplot(t[1:(N-1)], u_1[-N] - u_1[-1],geom = "line",xlab = 's',ylab = expression(Delta*Z),main='(b)')
real1d<-plot_grid(plot1, plot2, align='h')
ggsave(filename=here("results","real1d.pdf"), plot=real1d, width = 12, height = 5)
```

###Estimation from one simulated realization

```{r estimating beta0 and beta1}
u <- y*sim11$data[,2]

v <- v2 <- NULL
for(i in 1:m){
    index <- (1:(N/m)) + (i-1)*(N/m)
    ##estimate beta0
    fit <- optim(5,lik1,location = cbind(t[index],1),method = "Brent",
                 data = u[index], lower = 0, upper = 10, hessian = TRUE)
    v <- rbind(v,CI.1d(fit))
    ##estimate beta1
    fit2 <- optim(0,lik2,beta0 = v$value[i],location = cbind(t[index],1),method = "Brent",
                 data = u[index], lower = -15, upper = 15, hessian = TRUE)
    v2 <- rbind(v2,CI.1d(fit2))
}
```

###Computation time

```{r optim S0}
v <- v2 <- NULL
start_time <- Sys.time()
for(i in 1:m){
    index <- (1:(N/m)) + (i-1)*(N/m)
    ##estimate beta0
    fit <- optim(5,lik1,location = cbind(t[index],1),method = "Brent",
                 data = u[index], lower = 0, upper = 10, hessian = TRUE)
}
v <- rbind(v,CI.1d(fit))
end_time <- Sys.time()
optim_time_S0 <- end_time - start_time

```

```{r smooth}
mcloc <- (1:m)/m-1/(2*m)
h1 <- h2 <- (0.5 * sqrt(sum((mcloc[1] - mcloc[2])^2)))^2

theta <- data.frame(expected = rep(0,4*N),lower = rep(0,4*N),
                    upper = rep(0,4*N),type = rep(0,4*N),t = rep(1:200,4))
##S0 estimators
start_time <- Sys.time()
theta$expected[1:N] <- rep(v$value, each = 50) 
theta$lower[1:N] <- rep(v$lower, each = 50) 
theta$upper[1:N] <- rep(v$upper, each = 50)
end_time <- Sys.time()
smooth_time_S0 <- end_time - start_time


##WS0 estimators
weight1 <- weight.fun(h1,N,m)
start_time <- Sys.time()
for(i in 1:N){
    theta$expected[N + i] <- sum(weight1[i,] * v$value)
    theta$lower[N + i] <- sum(weight1[i,] * v$lower)
    theta$upper[N + i] <- sum(weight1[i,] * v$upper)
}
end_time <- Sys.time()
smooth_time_WS0 <- end_time - start_time
```

```{r optim NS1}
m=4
v <- v2 <- NULL
start_time <- Sys.time()
for(i in 1:m){
    index <- (1:(N/m)) + (i-1)*(N/m)
    ##estimate beta0
    fit <- optim(5,lik1,location = cbind(t[index],1),method = "Brent",
                 data = u[index], lower = 0, upper = 10, hessian = TRUE)
    v <- rbind(v,CI.1d(fit))
    ##estimate beta1
    fit2 <- optim(0,lik2,beta0 = v$value[i],location = cbind(t[index],1),method = "Brent",
                 data = u[index], lower = -15, upper = 15, hessian = TRUE)
    v2 <- rbind(v2,CI.1d(fit2))
}
end_time <- Sys.time()
optim_time_NS1 <- end_time - start_time
```

```{r smooth NS1}
mcloc <- (1:m)/m-1/(2*m)
h1 <- h2 <- (0.5 * sqrt(sum((mcloc[1] - mcloc[2])^2)))^2

theta <- data.frame(expected = rep(0,4*N),lower = rep(0,4*N),
                    upper = rep(0,4*N),type = rep(0,4*N),t = rep(1:200,4))
start_time <- Sys.time()
##NS1 estimators
weight2 <- weight.fun(h2,N,m)
for(i in 1:N){
    theta$expected[2*N + i] <- sum(weight2[i,] * (v$value + v2$value * (t[i] - mcloc)))
    theta$lower[2*N + i] <- sum(weight2[i,] * (v$lower + ifelse((t[i] - mcloc)>0,v2$lower,v2$upper) * (t[i] - mcloc)))
    theta$upper[2*N + i] <- sum(weight2[i,] * (v$upper + ifelse((t[i] - mcloc)>0,v2$upper,v2$lower) * (t[i] - mcloc)))
}

end_time <- Sys.time()
smooth_time_NS1 <- end_time - start_time
```

```{r moving window}
start_time <- Sys.time()
mov<-optim(5,lik1,location = cbind(t[index],1),method = "Brent",
                 data = u[index], lower = 0, upper = 10, hessian = TRUE)
end_time <- Sys.time()
optim_time_movS0 <- end_time - start_time
```

```{r}
time_S0 <- optim_time_S0 + smooth_time_S0
time_WS0 <- optim_time_S0 + smooth_time_WS0
time_NS1 <- optim_time_NS1 + smooth_time_NS1
time_movS0 <- optim_time_movS0*N
```

```{r multiple nonstationary parameters}
m=4
v <- v2 <- NULL
start_time <- Sys.time()
for(i in 1:m){
    index <- (1:(N/m)) + (i-1)*(N/m)
    ##estimate beta0
    fit <- optim(c(5,0.1,0.1),lik5,location = cbind(t[index],1),method = "L-BFGS-B",
                 data = u[index], lower = c(0,0,0.3), upper = 10, hessian = TRUE)
    ##estimate beta1
    fit2 <- optim(c(0,0,0),lik6,beta0 = fit$par,location = cbind(t[index],1),method = "L-BFGS-B", data = u[index],lower = c(-1,-1,-1), upper = c(1,1,1), hessian = TRUE)
}
end_time <- Sys.time()
optim_time_NS1 <- end_time - start_time

```


```{r approximating spatially varying parameter theta}
mcloc <- (1:m)/m-1/(2*m)
h1 <- h2 <- (0.5 * sqrt(sum((mcloc[1] - mcloc[2])^2)))^2

theta <- data.frame(expected = rep(0,3*N),lower = rep(0,3*N),
                    upper = rep(0,3*N),type = rep(0,3*N),t = rep(1:N,3))
##S0 estimators
theta$expected[1:N] <- rep(v$value, each = N/m) 
theta$lower[1:N] <- rep(v$lower, each = N/m) 
theta$upper[1:N] <- rep(v$upper, each = N/m)

##WS0 estimators
weight1 <- weight.fun(h1,N,m)
for(i in 1:N){
    theta$expected[N + i] <- sum(weight1[i,] * v$value)
    theta$lower[N + i] <- sum(weight1[i,] * v$lower)
    theta$upper[N + i] <- sum(weight1[i,] * v$upper)
}

##Real Curve
theta$expected[2*N + 1:N] <- y
theta$lower[2*N + 1:N] <- NA
theta$upper[2*N + 1:N] <- NA
theta$type<-c(rep("2:S0",N),rep("3:WS0",N),rep("1:Truth",N))

theta2 <- data.frame(expected = rep(0,2*N),lower = rep(0,2*N),
                    upper = rep(0,2*N),type = rep(0,2*N),t = rep(1:N,2))

##NS1 estimators
weight2 <- weight.fun(h2,N,m)
for(i in 1:N){
    theta2$expected[N + i] <- sum(weight2[i,] * (v$value + v2$value * (t[i] - mcloc)))
    theta2$lower[N + i] <- sum(weight2[i,] * (v$lower + ifelse((t[i] - mcloc)>0,v2$lower,v2$upper) * (t[i] - mcloc)))
    theta2$upper[N + i] <- sum(weight2[i,] * (v$upper + ifelse((t[i] - mcloc)>0,v2$upper,v2$lower) * (t[i] - mcloc)))
}
##Real Curve
theta2$expected[1:N] <- y
theta2$lower[1:N] <- NA
theta2$upper[1:N] <- NA
theta2$type<-c(rep("1:Truth",N),rep("2:NS1",N))
```

###Estimation from 1000 simulated realization

```{r 1000 times estimating beta0 and beta1}
##estimation
##local stationary
niters <- 100
v.vec <- v2.vec <- matrix(0,4,niters)
##Repeat 1000 times
for(rep in 1:niters){
    u <- y*sim11$data[,rep]
    for(i in 1:4){
        index <- (1:(N/m)) + (i-1)*(N/m)
        ##estimate beta0
        fit <- optim(5,lik1,location = cbind(t[index],1),method = "Brent",
                 data = u[index], lower = 0, upper = 10)
        ##estimate beta1
        fit2 <- optim(2,lik2, beta0 =  fit$par,location = cbind(t[index],1),
                      method = "Brent",data = u[index], lower = -15, upper = 15)
        v.vec[i,rep] <- fit$par
        v2.vec[i,rep] <- fit2$par
    }
}
```

###Save the results
```{r Save the results}
sims.1d <- cbind(v.vec,v2.vec)
saveRDS(sims.1d,here("results",'sims.1d.rds'))

```

```{r 1000 times approximating theta}
sims.1d <- readRDS(here("results","sims.1d.rds"))
v.vec <- sims.1d[, 1:100]
v2.vec <- sims.1d[, 101:200]

##smooth the estimators
theta.WS0 <- theta.NS1 <- matrix(0,niters,200)
for(j in 1:niters){
beta0 <- v.vec[,j]
beta1 <- v2.vec[,j]
    for(i in 1:N){
        ##WS0 estimators
        theta.WS0[j,i] <- sum(weight1[i,] * beta0)
        ##NS1 estimators
        theta.NS1[j,i] <- sum(weight2[i,] * (beta0 + beta1 * (t[i] - mcloc)))
    }

}
theta.S0 <- rep(beta0, each = 50) 
```

##Results

```{r results for table}
##Calculate the mean and standard deviation
beta0.mean <- round(apply(v.vec,1,mean),2)
beta1.mean <- round(apply(v2.vec,1,mean),2)
beta0.sd <- round(apply(v.vec,1,sd),2)
beta1.sd <- round(apply(v2.vec,1,sd),2)
theta.WS0.m <- theta.NS1.m <-c()
for(i in 1:N){
    ##WS0 estimators
    theta.WS0.m[i] <- sum(weight1[i,] * beta0.mean)
    ##NS1 estimators
    theta.NS1.m[i] <- sum(weight2[i,] * (beta0.mean + beta1.mean * (t[i] - mcloc)))
}

theta.S0.m <- rep(beta0.mean, each = 50) 
## Mean squared error
mse.WS0 <- round(mean((theta.WS0.m - y)^2),3)
mse.NS1 <- round(mean((theta.NS1.m - y)^2),3)
mse.S0 <- round(mean((theta.S0.m - y)^2),3)
mse.S0/mse.NS1
mse.WS0/mse.NS1
```

```{r results with CI 1 simulation}
p <- ggplot(data = theta, aes(x=t/200, y=expected, colour=type)) + 
    geom_line() + ylab(expression(sigma)) + xlab("s") +
    ggtitle("(a) Local Stationary Estimations, m=4") +
    scale_y_continuous(limits = c(0,7))+
    geom_ribbon(aes(ymin=lower, ymax=upper,fill=type), linetype=2, alpha=0.3) + 
    scale_color_brewer(palette = "Set1") +    
    scale_fill_brewer(palette = "Set1")
p
```

```{r}
p2 <- ggplot(data = theta2, aes(x=t/200, y=expected, colour=type)) + 
    geom_line() + ylab(expression(sigma)) + xlab("s") +
    ggtitle("(b) Our Estimation, m=4") +scale_y_continuous(limits = c(0,7))+
    geom_ribbon(aes(ymin=lower, ymax=upper,fill=type), linetype=2, alpha=0.3) + 
    scale_color_brewer(palette = "Set1") +    
    scale_fill_brewer(palette = "Set1")
p2
```

```{r save the figure}
combine_plot<-plot_grid(p, p2, align='h',rel_widths = 1.2, rel_heights = 1)
ggsave(filename=here("results","1Dest.pdf"),device='pdf', plot=combine_plot, width = 12, height = 5)
```

```{r save the figure}
combine_plot<-plot_grid(p, p2, align='h',rel_widths = 1.2, rel_heights = 1)
ggsave(filename=here("results","1Destm2.pdf"), plot=combine_plot, width = 12, height = 5)
```

```{r save the figure}
combine_plot<-plot_grid(p, p2, align='h',rel_widths = 1.2, rel_heights = 1)
ggsave(filename=here("results","1Destm4.pdf"), plot=combine_plot, width = 12, height = 5)
```

```{r save the figure}
combine_plot<-plot_grid(p, p2, align='h',rel_widths = 1.2, rel_heights = 1)
ggsave(filename=here("results","1Destm8.pdf"), plot=combine_plot, width = 12, height = 5)
```

```{r save the figure}
combine_plot<-plot_grid(p, p2, align='h',rel_widths = 1.2, rel_heights = 1)
ggsave(filename=here("results","1Destm10.pdf"), plot=combine_plot, width = 12, height = 5)
```

```{r fbplots 100 simultions}
par(mfrow=c(1,2),mar = c(4, 4, 2, 1))
##Functional boxplot
fbplot(t(theta.WS0),x = t,xlim = c(0,1),ylim = c(0,8),
       xlab = 's',ylab = expression(sigma),col = '#ACA4E2',barcol = '#ABB065',
       main = '(a) Functional boxplot -- WS0')
lines(t,y,col = 'red',lwd = 3,lty = 4)
legend('topright',c('Truth'),col = c('red'),
       lty = 4,lwd = 3,cex = 1,bty = "n")

fbplot(t(theta.NS1),x = t,xlim = c(0,1),ylim = c(0,8),
       xlab = 's',ylab = expression(sigma),col='#ACA4E2',
       barcol = '#ABB065',main = '(b) Functional boxplot -- NS1')
lines(t,y,col = 'red',lwd = 3,lty = 4)
legend('topright',c('Truth'),col = c('red'),
       lty = 4, lwd = 3,cex = 1,bty = "n")

```


