---
title: "2D simulation study"
author: "Yuxiao Li"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: true
  html_document:
    toc: true
    number_sections: true
    code_folding: hide
---

# Overview
This is the code for generating 2D nonstationary Gaussian random field with nonstationary kernel matrix. It includes 5 sections: "Libraries" to load the required library; "Functions" to write down the required functions for the estimation procedures; "Estimation", the main function, to generate Gaussian random field and estimate parameters; and "Results" to show the results including table and figures.

## Libraries

```{r load_libs}
library(geoR)
library(fda)
library(ggplot2)
library(cowplot)
library(stats4)
```

##Functions

```{r 2d generate theta}
##Function for parameter setups
theta <- function (n,beta0,beta1,beta2,beta3,beta4) {
    N <- sqrt(n)
    theta <- matrix(n,N,N)
    for(i in (1 : N)){
        for(j in (1 : N)){
            x1 <- i/N
            x2 <- j/N
            theta[i,j] <- beta0 + beta1*(x1 - .5) + beta2*(x2-.5) + 
            beta3*(x1 - .5)^2 + beta4*(x2 - .5)^2
        }
    }
  return(theta)
}
```

```{r 2d likelihood}
##function for likelihood estimation
##Input:
##locations: n by 2 matrix
##data: length n*m vector, m is the number of independent replicates
##params: spatial varying parameters, sigma
##p: S0 estimators using NSconvo
##Output:
##Log likelihood

local_loglik<- function (params,locations, data, p) 
{   
  fixed <- rep(FALSE,6 )
  params <- fixed
  function(s) {
    params[!fixed] <- s
    beta11 <- params[1]
    beta12 <- params[2]
    beta21 <- params[3]
    beta22 <- params[4]
    beta31  <- params[5]
    beta32  <- params[6]
    
    beta10 <- p[1]
    beta20 <- p[2]
    beta30 <- p[3]
    nu <- p[4]
    sigma2<-p[5]
    tau2<-p[6]
    N <- dim(locations)[1]
    m <- dim(data)[2]
    beta1 <- c(beta10,beta11,beta12)
    beta2 <- c(beta20,beta21,beta22)
    beta3 <- c(beta30,beta31,beta32)
    Xmat <- cbind(rep(1,N), locations - colMeans(locations))
    kernel.local <- array(0, dim = c(2, 2, N))
    for ( i in 1:N){
        lam1 <- exp(sum(Xmat[i,] * beta1))
        lam2 <- exp(sum(Xmat[i,] * beta2))
        phi <- (pi/2) * exp(sum(Xmat[i,] * beta3))/(1 + exp(sum(Xmat[i,] * beta3)))
        Pmat <- matrix(c(cos(phi), -sin(phi), sin(phi), cos(phi)), nrow = 2, byrow = T)
        Dmat <- diag(c(lam1, lam2))
        Sigma <- Pmat %*% Dmat %*% t(Pmat)
        kernel.local[, , i] <-  Sigma
    }
    Sigma.mat <- matrix(rep(NA, N^2), nrow = N)
    Q.mat <- matrix(rep(NA, N^2), nrow = N)
    Inv_ij <- matrix(rep(NA,4),2,2)
    for (i in 1:N) {
        Sigma.mat[i, i] <- 1
        Q.mat[i, i] <- 0
        Kernel_i <- kernel.local[, , i]
        det_i <- Kernel_i[1,1] * Kernel_i[2,2] - Kernel_i[1,2] * Kernel_i[2,1]
        if (i < N) {
            for (j in (i + 1):N) {
                Kernel_j <- kernel.local[, , j]
                det_j <- Kernel_j[1,1] * Kernel_j[2,2] - Kernel_j[1,2] * Kernel_j[2,1]
                Kernel_ij <- 0.5 * (Kernel_i + Kernel_j)
                Inv_ij[1,1] <- Kernel_ij[2,2] 
                Inv_ij[2,2] <- Kernel_ij[1,1] 
                Inv_ij[2,1] <- -Kernel_ij[2,1] 
                Inv_ij[1,2] <- -Kernel_ij[1,2] 
                det_ij <- Kernel_ij[1,1] * Kernel_ij[2,2] - Kernel_ij[1,2] * Kernel_ij[2,1]
                x <- locations[i, ] - locations[j, ]
                Sigma.mat[i, j] <- sqrt(sqrt(det_i * det_j)/det_ij)
                Q.mat[i, j] <- sqrt(t(x) %*% Inv_ij %*% x/det_ij)
                Sigma.mat[j, i] <- Sigma.mat[i, j]
                Q.mat[j, i] <- Q.mat[i, j]
            }
        }
    }
    
    cov <- geoR::cov.spatial(Q.mat, cov.model = "matern", 
                             cov.pars = c(sigma2, 1), kappa = nu)
    NS.cov <- Sigma.mat * cov + diag(rep(tau2,N))
    
    Eigen <- eigen(NS.cov)
    Eigen_value <- diag(Eigen$values)
    Eigen_vec <- Eigen$vectors
    Cov.inv <- Eigen_vec %*% diag(1/diag(Eigen_value)) %*% t(Eigen_vec)
    
    loglikelihood <-  m * sum(log(2*pi*diag(Eigen_value))) + 
        sum(diag(t(data) %*% Cov.inv %*% data))
    if (abs(loglikelihood) == Inf) loglikelihood <- 1e+06
    return(loglikelihood)
  }
}
```

```{r simulate cov}
##Function for simulating nonstaionary covariance
##grided on [0,1]^2 given spatially varying parameters
##Input:
##n: number of locations
##log.lam1: log of spatial range 1
##log.lam2: log of spatial range 2
##logit.phi: logit of rotation of anisotropy
##sigma2: variance
##tau2: nugget effect
##nu: smoothness
##Input:
##locations:n*2 matrix indicating locations
##NS.cov: Generated nonstationary covariance matrix
simulation <- function(n = 100,log.lam1 = NULL,log.lam2 = NULL, logit.phi = NULL, 
                      sigma2= NULL, tau2= NULL, nu = NULL){
    N <- sqrt(n)
  
    ##generate locations
    x1 <- (1:N)/N
    x2 <- (1:N)/N
    locations <- expand.grid(x1, x2)
    locations <- as.matrix(locations)
  
    kernel.local <- array(0, dim = c(2, 2, n))
    for(i in 1 : n){
        lam1 <- exp(log.lam1[i])
        lam2 <- exp(log.lam2[i])
        phi <- (pi/2)*exp(logit.phi[i])/(1+exp(logit.phi[i]))
        Pmat <- matrix(c(cos(phi), -sin(phi), sin(phi), cos(phi)), nrow = 2, byrow = T)
        Dmat <- diag(c(lam1, lam2))
        Sigma <- Pmat %*% Dmat %*% t(Pmat)
        kernel.local[, , i] <-  Sigma
    }

    ##Calculate Matern form Nonstationary Covariance function 
    Sigma.mat <- matrix(rep(NA, n^2), nrow = n)
    Q.mat <- matrix(rep(NA, n^2), nrow = n)
    Inv_ij <- matrix(rep(NA,4),2,2)
    for (i in 1:n) {
        Sigma.mat[i, i] <- 1
        Q.mat[i, i] <- 0
        Kernel_i <- kernel.local[, , i]
        det_i <- Kernel_i[1,1] * Kernel_i[2,2] - Kernel_i[1,2] * Kernel_i[2,1]
        if (i < n) {
            for (j in (i + 1):n) {
                Kernel_j <- kernel.local[, , j]
                det_j <- Kernel_j[1,1] * Kernel_j[2,2] - Kernel_j[1,2] * Kernel_j[2,1]
                Kernel_ij <- 0.5 * (Kernel_i + Kernel_j)
                Inv_ij[1,1] <- Kernel_ij[2,2] 
                Inv_ij[2,2] <- Kernel_ij[1,1] 
                Inv_ij[2,1] <- - Kernel_ij[2,1] 
                Inv_ij[1,2] <- - Kernel_ij[1,2] 
                det_ij <- Kernel_ij[1,1] * Kernel_ij[2,2] - Kernel_ij[1,2] * Kernel_ij[2,1]
                x <- locations[i, ] - locations[j, ]
                Sigma.mat[i, j] <- sqrt(sqrt(det_i * det_j)/det_ij)
                Q.mat[i, j] <- sqrt(t(x) %*% Inv_ij %*% x/det_ij)
                Sigma.mat[j, i] <- Sigma.mat[i, j]
                Q.mat[j, i] <- Q.mat[i, j]
            }
        }
    }
    cov <- geoR::cov.spatial(Q.mat, cov.model = "matern", 
                           cov.pars = c(sigma2, 1), kappa = nu)
    NS.cov <- Sigma.mat * cov + diag(rep(tau2,n))
  
    return(list(locations = locations,NS.cov = NS.cov,kernel.local=kernel.local))
}
```

```{r 2d initial}
library(convoSPAT)
library(geoR)
library(fields)

##Parameter setups
n<-400
N<-sqrt(n)
log.lam1<-theta(n,-3,0,0,-6,-7)
log.lam2<-theta(n,-5,0,0,6,-4)
logit.phi<-theta(n,0,1,-2,0,1)
sigma2 <- 1
tau2 <- .1
nu <- 2

##Plot the nonstationary parameters
par(mfrow = c(2,2),mar = c(3, 3, 1, 1),mgp = c(1.5,.5,0))
par(mfrow=c(2,2), mar = c(2.2,3,2,0.5), mgp = c(1.3,.5,0))
image.plot(exp(log.lam1),zlim = c(0,.05),xlab = expression(s[1]),ylab = expression(s[2]))
title(main = list(expression(lambda[1]),cex = 1.5,font = 5))

image.plot(exp(log.lam2),zlim = c(0,0.031),xlab = expression(s[1]),ylab = expression(s[2]))
title(main = list(expression(lambda[2]),cex = 1.5,font = 5))

image.plot(pi/2 * exp(logit.phi)/(1 + exp(logit.phi)),zlim = c(0.3,1.3),
           xlab = expression(s[1]),ylab = expression(s[2]))
title(main = list(expression(phi),cex = 1.5,font = 5))

##Generate Random Fields
real <- simulation(n = n, log.lam1 = c(log.lam1),log.lam2 = c(log.lam2), 
                   logit.phi = c(logit.phi), sigma2= sigma2, tau2 = tau2, nu = nu)

###  true contours and images for covariance function
NS.cov <- real$NS.cov
image.plot(NS.cov,xaxt = 'n',yaxt = 'n',ylim = c(1,0),main = 'Covariance Matrix')

par(mfrow=c(2,2))
par(mar = c(3, 3, 1.2, 1))
nf <- layout(matrix(c(1,1,0,0,2,2,1,1,3,3,2,2,4,4,3,3,5,5,4,4,0,0,5,5), 6, 4),respect = F)
layout.show(nf)

NS.corner1 <- matrix(NS.cov[10,],sqrt(n),sqrt(n),byrow = T)
image(NS.corner1,col = topo.colors(64),
      xlab = expression(s[1]),ylab = expression(s[2]),main = 'Left')
contour(NS.corner1,add = T)

NS.corner2 <- matrix(NS.cov[390,],sqrt(n),sqrt(n),byrow = T)
image(NS.corner2,col = topo.colors(64),
      xlab = expression(s[1]),ylab = expression(s[2]),main = 'Right')
contour(NS.corner2,add = T)

NS.corner3 <- matrix(NS.cov[170,],sqrt(n),sqrt(n),byrow = T)
image(NS.corner3,col = topo.colors(64),
        xlab = expression(s[1]),ylab = expression(s[2]),main = 'Center')
contour(NS.corner3,add = T)

NS.corner4 <- matrix(NS.cov[200,],sqrt(n),sqrt(n),byrow = T)
image(NS.corner4,col = topo.colors(64),
      xlab = expression(s[1]),ylab = expression(s[2]),main = 'Top')
contour(NS.corner4,add = T)
  
NS.corner5 <- matrix(NS.cov[181,],sqrt(n),sqrt(n),byrow = T)
image(NS.corner5,col = topo.colors(64),
      xlab = expression(s[1]),ylab = expression(s[2]),main = 'Bottom')
contour(NS.corner5,add = T)

```

```{r 2d step 1}
###  Local stationary estimation
N.mc <- 4
fit.radius <- 0.29
rslt <- NSconvo_fit(coords = real$locations,data = t(real$sim.data),
                    cov.model = "matern",fit.radius = fit.radius, N.mc = N.mc)

## Local stationary Estimators  
mc.locations <- rslt$mc.locations
beta0_lam1 <- rslt$MLEs.save$lam1
beta0_lam2 <- rslt$MLEs.save$lam2
beta0_phi <- rslt$MLEs.save$eta
sigma2.est <- rslt$sigmasq.est
tau2.est <- rslt$tausq.est
nu.est <- rslt$kappa.MLE
h <- rslt$lambda.w
p <- matrix(0,N.mc,6)
for (i in 1:N.mc) {
    p[i,] <- c(log(beta0_lam1[i]),log(beta0_lam2[i]),log(beta0_phi[i]/(pi/2 - beta0_phi[i])),
               nu.est,sigma2.est,tau2.est)
}

#saveRDS(p,"p_2d.Rda")
#saveRDS(mc.locations,"mc.locations.Rda")
```

```{r 2d step 2 option1}
## Divide by Square
nk <- N.mc
Nk <- sqrt(nk)
nkr <- n/nk
NKR <- sqrt(nkr)
local.index <- rep(0, nkr)
for(j in 1:NKR){
    local.index[(1 + (j - 1) * NKR):(j * NKR)] <- (1 + (j - 1) * Nk * NKR):(((j - 1) * Nk * NKR) + NKR)
}
LL.est <- matrix(0,nk,6)

for(l in 1 : Nk){
    for (k in 1 : Nk) {
        index <- (k-1)*NKR+ local.index + Nk*nkr*(l-1)
        temp.locations<- real$locations[index,]
        temp.data<- t(real$sim.data)[index,]
        make.local.loglik <- local_loglik(locations = temp.locations, 
                                          data = temp.data, p = p[l+(k-1)*Nk,]) 
        MLEs.local <- optim(c(0,0,0,0,0,0), make.local.loglik, method="BFGS")
        if (MLEs.local$convergence != 0) {
            if (MLEs.local$convergence == 52) {
                cat(paste("  There was a NON-FATAL error with optim(): \n  ", 
                    MLEs.local$convergence, "  ", MLEs.local$message, "\n", 
                    sep = ""))
            }
            else {
                cat(paste("  There was an error with optim(): \n  ", 
                          MLEs.local$convergence, "  ", MLEs.local$message, "\n",
                          sep = ""))
            }
        }
    LL.est[l+(k-1)*Nk,]<-MLEs.local$par
    }
}

LL.est<-LL.est.circle
```

```{r 2d step 2 option2}

##Or Divide by Circle

LL.est.circle <- matrix(0,N.mc,6)
for (k in 1:N.mc) {
    d1<-abs(real$locations[, 1] - mc.locations[k, 1])
    d2<-abs(real$locations[, 2] - mc.locations[k, 2])
    temp.locs <- real$locations[(d1 <= fit.radius) & (d2 <= fit.radius), ]
    temp.dat <- real$sim.data[,(d1 <= fit.radius) & (d2 <= fit.radius) ]
    distances <- rep(NA, dim(temp.locs)[1])
    for (i in 1:dim(temp.locs)[1]) {
        distances[i] <- sqrt(sum((temp.locs[i, ] - mc.locations[k, ])^2))
    }
    temp.locations <- temp.locs[distances <= fit.radius, ]
    n.fit <- dim(temp.locations)[1]
    temp.dat <- as.matrix(temp.dat, nrow = n.fit)
    temp.data <- temp.dat[,distances <= fit.radius ]
    temp.data <- as.matrix(temp.data, nrow = n.fit)
    if (k == 1) {
        cat("Calculating the linear terms for:\n")
    }
    cat("mixture component location ", k, ", using ", 
        n.fit, " observations...\n", sep = "")
    make.local.loglik <- local_loglik(locations = temp.locations, 
                                      data = t(temp.data), p = p[k,]) 
    MLEs.local <- optim(c(0,0,0,0,0,0), make.local.loglik, 
                        method="L-BFGS-B", lower = -10, upper = 10)
    if (MLEs.local$convergence != 0) {
        if (MLEs.local$convergence == 52) {
        cat(paste("  There was a NON-FATAL error with optim(): \n  ", 
                  MLEs.local$convergence, "  ", MLEs.local$message, "\n", 
                  sep = ""))
        }
        else {
        cat(paste("  There was an error with optim(): \n  ", 
                  MLEs.local$convergence, "  ", MLEs.local$message, "\n", 
                  sep = ""))
        }
    }
    LL.est.circle[k,]<-MLEs.local$par
}

LL.est<-LL.est.circle
```

```{r 2d results}
##  Smooth the estimators
lam1.est <- lam2.est <- phi.est <- matrix(0,N,N)
lam1.est.ll <- lam2.est.ll <- phi.est.ll <- matrix(0,N,N)
weights <-  array(0,c(N,N,N.mc))
for(i in (1 : N)){
    for(j in (1 : N)){
        x1 <- i/N
        x2 <- j/N
        for(k in 1:N.mc) {
            weights[i,j,k] < -exp(-sum((c(x1,x2) - mc.locations[k,])^2)/2/h)
        }
        weights[i,j,] <- weights[i,j,]/sum(weights[i,j,])
        ##WS0 estimators
        lam1.est[i,j] <- sum(weights[i,j,] * p[,1])
        lam2.est[i,j] <- sum(weights[i,j,] * p[,2])
        phi.est[i,j] <- sum(weights[i,j,] * p[,3])
        ##NS1 estimators
        lam1.est.ll[i,j] <- sum(weights[i,j,] * (p[,1] + 
                                                LL.est[,1] * (x1 - mc.locations[,1]) +
                                                LL.est[,2] * (x2-mc.locations[,2])))
        lam2.est.ll[i,j] <- sum(weights[i,j,] * (p[,2] + 
                                                LL.est[,3] * (x1 - mc.locations[,1]) + 
                                                LL.est[,4] * (x2-mc.locations[,2])))
        phi.est.ll[i,j] <- sum(weights[i,j,] * (p[,3] + 
                                                LL.est[,5] * (x1 - mc.locations[,1]) +
                                                LL.est[,6]*(x2-mc.locations[,2])))
    }
}
  
##Compare contours
Sigma.est <- array(0,dim = c(n,2,2))
for (q in 1:n){
    eigenvec <- pi/2 * exp(c(phi.est)[q])/(1 + exp(c(phi.est)[q]))
    eigenval <- exp(c(c(lam1.est)[q], c(lam2.est)[q]))
    Pmat.est <- matrix(c(cos(eigenvec), -sin(eigenvec), 
                         sin(eigenvec), cos(eigenvec)),2, 2 ,byrow = T)
    Dmat.est <- diag(eigenval)
    Sigma.est[q,,] <- Pmat.est %*% Dmat.est %*% t(Pmat.est)
}
Sigma.est.ll <- array(0,dim = c(n,2,2))
for (q in 1:n){
    eigenvec <- pi/2 * exp(c(phi.est.ll)[q])/(1 + exp(c(phi.est.ll)[q]))
    eigenval <- exp(c(c(lam1.est.ll)[q], c(lam2.est.ll)[q]))
    Pmat.est.ll <- matrix(c(cos(eigenvec), -sin(eigenvec), 
                            sin(eigenvec), cos(eigenvec)),2, 2, byrow = T)
    Dmat.est.ll <- diag(eigenval)
    Sigma.est.ll[q,,] <- Pmat.est.ll %*% Dmat.est.ll %*% t(Pmat.est.ll)
}
  
par(mar = c(3, 3, 1, 1), mgp = c(1.5,.5,0))
nf <- layout(matrix(c(1,1,0,0,2,2,1,1,3,3,2,2,4,4,3,3,5,5,4,4,0,0,5,5), 6, 4),respect = F)

for(pp in c(1,20,170,381,400)) {
    plot(ellipse::ellipse(real$kernel.local[,,pp],
                          centre=c(real$locations[pp,])),
         col='black',type='l',lwd=1,lty=1,xlim=c(-.2,1.2),ylim=c(-.2,1.2),
         xlab = expression(s[1]),ylab=expression(s[2]))
    points(real$locations[pp,][1],real$locations[pp,][2],pch=16)
    lines(ellipse::ellipse(Sigma.est[pp,,],centre = c(real$locations[pp,])),
          col='green',lwd=2,lty=2)
    lines(ellipse::ellipse(Sigma.est.ll[pp,,],centre = c(real$locations[pp,])),
          col='red',lwd=2,lty=3)
    if (pp == 20|pp == 400){
        legend('topleft',c("Truth","WS0","NS1"),col=c('black','green','red'),lwd=c(1,2,2),lty=c(1,2,3),bty='n')
    }             
    else {
        legend('bottomright',c("Truth","WS0","NS1"),col=c('black','green','red'),lwd=c(1,2,2),lty=c(1,2,3),bty='n')
    }
}
  
##Compare estimators
par(mfrow = c(3,3))
image.plot(exp(log.lam1),xlab = 'x coordiate',ylab = 'y coordiate',
           main = expression('true'~ lambda~'_1'))
contour(exp(log.lam1),add = T)

image.plot(exp(log.lam2),xlab = 'x coordiate',ylab = 'y coordiate',
           main = expression('true'~lambda~'_2'))
contour(exp(log.lam2),add=T)
  
image.plot(pi/2 * exp(logit.phi)/(1 + exp(logit.phi)),xlab = 'x coordiate',
           ylab = 'y coordiate',main = expression('true'~ phi))
contour(pi/2 * exp(logit.phi)/(1 + exp(logit.phi)),add = T)
  
image.plot(exp(lam1.est),xlab = 'x coordiate',ylab = 'y coordiate',
           main = expression('local stationary estimation of'~ lambda~'_1'))
contour(exp(lam1.est),add = T)

image.plot(exp(lam2.est),xlab = 'x coordiate',ylab = 'y coordiate',
           main = expression('local stationary estimation of'~ lambda~'_2'))
contour(exp(lam2.est),add = T)

image.plot(pi/2 * exp(phi.est)/(1 + exp(phi.est)),xlab='x coordiate',ylab='y coordiate',
           main = expression('local stationary estimation of'~ ~ phi))
contour(pi/2*exp(phi.est)/(1+exp(phi.est)),add = T)

image.plot(exp(lam1.est.ll),xlab = 'x coordiate',ylab = 'y coordiate',
           main = expression('first order nonstationary estimation of'~ lambda~'_1'))
contour(exp(lam1.est.ll),add = T)

image.plot(exp(lam2.est.ll),xlab = 'x coordiate',ylab = 'y coordiate', 
           main=expression('first order nonstationary estimation of'~ lambda~'_2'))
contour(exp(lam2.est.ll),add = T)
image.plot(pi/2 * exp(phi.est.ll)/(1 + exp(phi.est.ll)),xlab = 'x coordiate',
           ylab='y coordiate',main=expression('first order nonstationary estimation of'~ phi))
contour(pi/2 * exp(phi.est.ll)/(1 + exp(phi.est.ll)),add = T)
  
  
## relative Error
sims <- simulation(n = n, log.lam1 = c(lam1.est),log.lam2 = c(lam2.est), 
                   logit.phi = c(phi.est),sigma2 = sigma2, tau2= tau2, nu = nu)
LScov <- sims$NS.cov
Es <- sum((NS.cov - LScov)^2)/sum(NS.cov^2)
sims.ll <- simulation(n = n, log.lam1 = c(lam1.est.ll),log.lam2 = c(lam2.est.ll), 
                      logit.phi = c(phi.est.ll), sigma2 = sigma2, tau2= tau2, nu = nu)
LLcov <- sims.ll$NS.cov
Es1 <- sum((NS.cov - LLcov)^2)/sum(NS.cov^2)
par(mfrow = c(1,3))
image.plot(NS.cov,xaxt = 'n',yaxt = 'n',main = 'Truth')
image.plot(LLcov,xaxt = 'n',yaxt = 'n',main = 'Local stationary Model')
image.plot(LScov,xaxt = 'n',yaxt = 'n',main = 'First order nonstaionary model')

Es-Es1
  
```

```{r function for repeating estimations 100 times in parellel}
library(parallel)
no_cores <- detectCores() - 6
cl <- makeCluster(no_cores)

nsfit<-function(rep){
theta <- function (n,beta0,beta1,beta2,beta3,beta4) {
    N <- sqrt(n)
    theta <- matrix(n,N,N)
    for(i in (1 : N)){
        for(j in (1 : N)){
            x1 <- i/N
            x2 <- j/N
            theta[i,j] <- beta0 + beta1*(x1 - .5) + beta2*(x2-.5) + 
            beta3*(x1 - .5)^2 + beta4*(x2 - .5)^2
        }
    }
  return(theta)
}

simulation <- function(n = 100,log.lam1 = NULL,log.lam2 = NULL, logit.phi = NULL, 
                      sigma2= NULL, tau2= NULL, nu = NULL){
    N <- sqrt(n)
  
    ##generate locations
    x1 <- (1:N)/N
    x2 <- (1:N)/N
    locations <- expand.grid(x1, x2)
    locations <- as.matrix(locations)
  
    kernel.local <- array(0, dim = c(2, 2, n))
    for(i in 1 : n){
        lam1 <- exp(log.lam1[i])
        lam2 <- exp(log.lam2[i])
        phi <- (pi/2)*exp(logit.phi[i])/(1+exp(logit.phi[i]))
        Pmat <- matrix(c(cos(phi), -sin(phi), sin(phi), cos(phi)), nrow = 2, byrow = T)
        Dmat <- diag(c(lam1, lam2))
        Sigma <- Pmat %*% Dmat %*% t(Pmat)
        kernel.local[, , i] <-  Sigma
    }

    ##Calculate Matern form Nonstationary Covariance function 
    Sigma.mat <- matrix(rep(NA, n^2), nrow = n)
    Q.mat <- matrix(rep(NA, n^2), nrow = n)
    Inv_ij <- matrix(rep(NA,4),2,2)
    for (i in 1:n) {
        Sigma.mat[i, i] <- 1
        Q.mat[i, i] <- 0
        Kernel_i <- kernel.local[, , i]
        det_i <- Kernel_i[1,1] * Kernel_i[2,2] - Kernel_i[1,2] * Kernel_i[2,1]
        if (i < n) {
            for (j in (i + 1):n) {
                Kernel_j <- kernel.local[, , j]
                det_j <- Kernel_j[1,1] * Kernel_j[2,2] - Kernel_j[1,2] * Kernel_j[2,1]
                Kernel_ij <- 0.5 * (Kernel_i + Kernel_j)
                Inv_ij[1,1] <- Kernel_ij[2,2] 
                Inv_ij[2,2] <- Kernel_ij[1,1] 
                Inv_ij[2,1] <- - Kernel_ij[2,1] 
                Inv_ij[1,2] <- - Kernel_ij[1,2] 
                det_ij <- Kernel_ij[1,1] * Kernel_ij[2,2] - Kernel_ij[1,2] * Kernel_ij[2,1]
                x <- locations[i, ] - locations[j, ]
                Sigma.mat[i, j] <- sqrt(sqrt(det_i * det_j)/det_ij)
                Q.mat[i, j] <- sqrt(t(x) %*% Inv_ij %*% x/det_ij)
                Sigma.mat[j, i] <- Sigma.mat[i, j]
                Q.mat[j, i] <- Q.mat[i, j]
            }
        }
    }
    cov <- geoR::cov.spatial(Q.mat, cov.model = "matern", 
                           cov.pars = c(sigma2, 1), kappa = nu)
    NS.cov <- Sigma.mat * cov + diag(rep(tau2,n))
  
    return(list(locations = locations,NS.cov = NS.cov))
}

local_loglik<- function (params,locations, data, p) 
{   
  fixed <- rep(FALSE,6 )
  params <- fixed
  function(s) {
    params[!fixed] <- s
    beta11 <- params[1]
    beta12 <- params[2]
    beta21 <- params[3]
    beta22 <- params[4]
    beta31  <- params[5]
    beta32  <- params[6]
    
    beta10 <- p[1]
    beta20 <- p[2]
    beta30 <- p[3]
    nu <- p[4]
    sigma2<-p[5]
    tau2<-p[6]
    N <- dim(locations)[1]
    m <- dim(data)[2]
    beta1 <- c(beta10,beta11,beta12)
    beta2 <- c(beta20,beta21,beta22)
    beta3 <- c(beta30,beta31,beta32)
    Xmat <- cbind(rep(1,N), locations - colMeans(locations))
    kernel.local <- array(0, dim = c(2, 2, N))
    for ( i in 1:N){
        lam1 <- exp(sum(Xmat[i,] * beta1))
        lam2 <- exp(sum(Xmat[i,] * beta2))
        phi <- (pi/2) * exp(sum(Xmat[i,] * beta3))/(1 + exp(sum(Xmat[i,] * beta3)))
        Pmat <- matrix(c(cos(phi), -sin(phi), sin(phi), cos(phi)), nrow = 2, byrow = T)
        Dmat <- diag(c(lam1, lam2))
        Sigma <- Pmat %*% Dmat %*% t(Pmat)
        kernel.local[, , i] <-  Sigma
    }
    Sigma.mat <- matrix(rep(NA, N^2), nrow = N)
    Q.mat <- matrix(rep(NA, N^2), nrow = N)
    Inv_ij <- matrix(rep(NA,4),2,2)
    for (i in 1:N) {
        Sigma.mat[i, i] <- 1
        Q.mat[i, i] <- 0
        Kernel_i <- kernel.local[, , i]
        det_i <- Kernel_i[1,1] * Kernel_i[2,2] - Kernel_i[1,2] * Kernel_i[2,1]
        if (i < N) {
            for (j in (i + 1):N) {
                Kernel_j <- kernel.local[, , j]
                det_j <- Kernel_j[1,1] * Kernel_j[2,2] - Kernel_j[1,2] * Kernel_j[2,1]
                Kernel_ij <- 0.5 * (Kernel_i + Kernel_j)
                Inv_ij[1,1] <- Kernel_ij[2,2] 
                Inv_ij[2,2] <- Kernel_ij[1,1] 
                Inv_ij[2,1] <- -Kernel_ij[2,1] 
                Inv_ij[1,2] <- -Kernel_ij[1,2] 
                det_ij <- Kernel_ij[1,1] * Kernel_ij[2,2] - Kernel_ij[1,2] * Kernel_ij[2,1]
                x <- locations[i, ] - locations[j, ]
                Sigma.mat[i, j] <- sqrt(sqrt(det_i * det_j)/det_ij)
                Q.mat[i, j] <- sqrt(t(x) %*% Inv_ij %*% x/det_ij)
                Sigma.mat[j, i] <- Sigma.mat[i, j]
                Q.mat[j, i] <- Q.mat[i, j]
            }
        }
    }
    
    cov <- geoR::cov.spatial(Q.mat, cov.model = "matern", 
                             cov.pars = c(sigma2, 1), kappa = nu)
    NS.cov <- Sigma.mat * cov + diag(rep(tau2,N))
    
    Eigen <- eigen(NS.cov)
    Eigen_value <- diag(Eigen$values)
    Eigen_vec <- Eigen$vectors
    Cov.inv <- Eigen_vec %*% diag(1/diag(Eigen_value)) %*% t(Eigen_vec)
    
    loglikelihood <-  m * sum(log(diag(Eigen_value))) + 
        sum(diag(t(data) %*% Cov.inv %*% data))
    if (abs(loglikelihood) == Inf) loglikelihood <- 1e+06
    return(loglikelihood)
  }
}
n <- 400
log.lam1 <- theta(n,-3,0,0,-6,-7)
log.lam2 <- theta(n,-5,0,0,6,-4)
logit.phi <- theta(n,0,1,-2,0,1)
  sigma2 <- 1
  tau2 <- .1
  nu <- 2
real <- simulation(n = n, log.lam1 = c(log.lam1),log.lam2 = c(log.lam2), 
                   logit.phi = c(logit.phi), 
                   sigma2= sigma2, tau2= tau2, nu = nu)
N.mc <- 4
fit.radius <- 0.29
rslt <- NSconvo_fit(coords = real$locations,data = t(real$sim.data),cov.model = "matern",fit.radius = fit.radius, N.mc = N.mc)
mc.locations <- rslt$mc.locations
beta0_lam1 <- rslt$MLEs.save$lam1
beta0_lam2 <- rslt$MLEs.save$lam2
beta0_phi <- rslt$MLEs.save$eta
sigma2.est <- rslt$sigmasq.est
tau2.est <- rslt$tausq.est
nu.est <- rslt$kappa.MLE
h <- rslt$lambda.w
p <- matrix(0,N.mc,6)
for (i in 1:N.mc) p[i,] <-c(log(beta0_lam1[i]),log(beta0_lam2[i]),
                            log(beta0_phi[i]/(pi/2-beta0_phi[i])),
                            nu.est,sigma2.est,tau2.est)

LL.est.circle <- matrix(0,N.mc,6)
for (k in 1:N.mc) {
    d1<-abs(real$locations[, 1] - mc.locations[k, 1])
    d2<-abs(real$locations[, 2] - mc.locations[k, 2])
    temp.locs <- real$locations[(d1 <= fit.radius) & (d2 <= fit.radius), ]
    temp.dat <- real$sim.data[,(d1 <= fit.radius) & (d2 <= fit.radius) ]
    distances <- rep(NA, dim(temp.locs)[1])
    for (i in 1:dim(temp.locs)[1]) {
        distances[i] <- sqrt(sum((temp.locs[i, ] - mc.locations[k, ])^2))
    }
    temp.locations <- temp.locs[distances <= fit.radius, ]
    n.fit <- dim(temp.locations)[1]
    temp.dat <- as.matrix(temp.dat, nrow = n.fit)
    temp.data <- temp.dat[,distances <= fit.radius ]
    temp.data <- as.matrix(temp.data, nrow = n.fit)
    if (k == 1) {
        cat("Calculating the linear terms for:\n")
    }
    cat("mixture component location ", k, ", using ", 
        n.fit, " observations...\n", sep = "")
    make.local.loglik <- local_loglik(locations = temp.locations, 
                                      data = t(temp.data), p = p[k,]) 
    MLEs.local <- optim(c(0,0,0,0,0,0), make.local.loglik, 
                        method="L-BFGS-B", lower = -10, upper = 10)
    if (MLEs.local$convergence != 0) {
        if (MLEs.local$convergence == 52) {
        cat(paste("  There was a NON-FATAL error with optim(): \n  ", 
                  MLEs.local$convergence, "  ", MLEs.local$message, "\n", 
                  sep = ""))
        }
        else {
        cat(paste("  There was an error with optim(): \n  ", 
                  MLEs.local$convergence, "  ", MLEs.local$message, "\n", 
                  sep = ""))
        }
    }
    LL.est.circle[k,]<-MLEs.local$par
}
est<-cbind(p,LL.est.circle)
return(est)
}

```

```{r 2d results 100 times}
n <- 400
rep <- 100
ns.result <- parLapply(cl, 1:rep ,nsfit)
#setwd("~/Documents")
#saveRDS(ns.result,"2dsims-100-new.rds")
ns.result<-readRDS("/Users/liy0h/Dropbox/My Research/Nonstationary paper/code/2dsims-100-new.rds")
LL.array <- array(0,c(4,12,rep))
for(i in 1:100) LL.array[,,i] <- ns.result[[i]]

##most representative curve
#mm<-matrix(0,4,12)
#index<-c()
#for(j in 1:4){
#index<-fbplot(LL.array[j,,],method = "Both",plot=F)$medcurve
#mm[j,]<-LL.array[j,,index]
#}
#p<-mm[,1:3]
#LL.est<-mm[,7:12]

##Mean curve
p <- apply(LL.array,c(1,2),mean)[,1:3]
LL.est <- apply(LL.array,c(1,2),mean)[,7:12]

####
mc.locations <- readRDS("/Users/liy0h/Documents/mc.locations.Rda")
##  
N=20
N.mc=4
lam1.est <- lam2.est <- phi.est <- matrix(0,N,N)
lam1.est.ll <- lam2.est.ll <- phi.est.ll <- matrix(0,N,N)
weights <- array(0,c(N,N,N.mc))
h = .0564
for(i in (1 : N)){
    for(j in (1 : N)){
        x1 <- i/N
        x2 <- j/N
        for(k in 1:N.mc) {
            weights[i,j,k]<-exp(-sum((c(x1,x2)-mc.locations[k,])^2)/2/h)
        }
    weights[i,j,] <- weights[i,j,]/sum(weights[i,j,])
    lam1.est[i,j] <- sum(weights[i,j,] * p[,1])
    lam2.est[i,j] <- sum(weights[i,j,] * p[,2])
    phi.est[i,j] <- sum(weights[i,j,] * p[,3])
    lam1.est.ll[i,j] <- sum(weights[i,j,] * (p[,1] + 
                                            LL.est[,1] * (x1 - mc.locations[,1]) + 
                                            LL.est[,2] * (x2-mc.locations[,2])))
    lam2.est.ll[i,j] <- sum(weights[i,j,] * (p[,2] + 
                                            LL.est[,3]*(x1-mc.locations[,1]) +
                                            LL.est[,4]*(x2-mc.locations[,2])))
    phi.est.ll[i,j] <- sum(weights[i,j,] * (p[,3] + 
                                            LL.est[,5]*(x1-mc.locations[,1]) +
                                            LL.est[,6]*(x2-mc.locations[,2])))
    }
}

##Function for generating S0
theta1 <- function (nk,beta0) {
    theta <- NULL
    Nk <- sqrt(nk)
    nn<-10
    for(k in (1 : Nk)){
        theta.col <- NULL
        for(l in (1 : Nk))
        {  
            theta.local <- matrix(0,nn,nn)
            for(i in (1 : nn)){
                for(j in (1 : nn)){
                    x1 <-i/nn
                    x2 <-j/nn
                    theta.local[i,j]<-beta0[l+(k-1)*Nk] 
                }
            }
            theta.col <- rbind(theta.col,theta.local)
        }
        theta <- cbind(theta,theta.col)
    }
    return(theta)
}

par(mfrow=c(3,3), mar = c(2,2.2,1,1), mgp = c(1.6,.5,0))

image.plot(exp(theta1(4,p[,1])),zlim = c(0,.05))
title(main = list(expression(lambda[1]), cex = 1.3,font = 2),
      xlab = list(expression(s[1]), cex = 1.5,font = 3),
      ylab = list("S0 estimates", cex = 1.5,font = 1))
#contour(exp(theta1(4,p[,1])),add = T)

image.plot(exp(theta1(4,p[,2])),zlim = c(0,0.031))
title(main = list(expression(lambda[2]), cex = 1.3,font = 2),
      xlab = list(expression(s[1]), cex = 1.5,font = 3),
      ylab = list(expression(s[2]), cex = 1.5,font = 3))
#contour(exp(theta1(4,p[,2])),add = T)

image.plot(pi/2 * exp(theta1(4,p[,3]))/(1 + exp(theta1(4,p[,3]))),zlim = c(0.3,1.3))
title(main = list(expression(phi),cex = 1.3,font = 2),
      xlab = list(expression(s[1]), cex = 1.5, font = 3),
      ylab=list(expression(s[2]), cex = 1.5, font = 3))
#contour(pi/2 * exp(theta1(4,p[,3]))/(1 + exp(theta1(4,p[,3]))),add = T)

image.plot(exp(lam1.est),zlim = c(0,0.055))
title(ylab = list("WS0 estimates", cex = 1.5, font = 1),
      xlab=list(expression(s[1]), cex = 1.5, font = 3))
#contour(exp(lam1.est),add = T)

image.plot(exp(lam2.est),zlim = c(0,0.031))
title(xlab = list(expression(s[1]), cex = 1.5, font = 3),
      ylab = list(expression(s[2]), cex = 1.5, font = 3))
#contour(exp(lam2.est),add = T)

image.plot(pi/2 * exp(phi.est)/(1 + exp(phi.est)),zlim = c(0.3,1.3))
#contour(pi/2 * exp(phi.est)/(1 + exp(phi.est)),add = T)
title(xlab = list(expression(s[1]), cex = 1.5, font = 3),
      ylab = list(expression(s[2]), cex = 1.5, font = 3))

image.plot(exp(lam1.est.ll),zlim = c(0,0.055))
title(ylab = list("NS1 estimates", cex = 1.5, font = 1),
      xlab = list(expression(s[1]), cex = 1.5, font = 3))
#contour(exp(lam1.est.ll),add = T)

image.plot(exp(lam2.est.ll),zlim = c(0,0.031))
title(xlab = list(expression(s[1]), cex = 1.5, font = 3),
      ylab=list(expression(s[2]), cex = 1.5, font = 3))
#contour(exp(lam2.est.ll),add = T)

image.plot(pi/2 * exp(phi.est.ll)/(1 + exp(phi.est.ll)),zlim = c(0.3,1.3))
title(xlab=list(expression(s[1]), cex = 1.5, font = 3),
      ylab=list(expression(s[2]), cex = 1.5, font = 3))
#contour(pi/2 * exp(phi.est.ll)/(1 + exp(phi.est.ll)),add = T)

```

```{r}
log.lam1<-theta(n,-3,0,0,-6,-7)
log.lam2<-theta(n,-5,0,0,6,-4)
logit.phi<-theta(n,0,1,-2,0,1)

MSE.S0.lam1<-mean((theta1(4,p[,1])-log.lam1)^2)
MSE.S0.lam2 <-mean((theta1(4,p[,2])-log.lam2)^2)
MSE.S0.phi <-mean((theta1(4,p[,2])-logit.phi)^2)
MSE.WS0.lam1<-mean((lam1.est-log.lam1)^2)
MSE.WS0.lam2<-mean((lam2.est-log.lam2)^2)
MSE.WS0.phi<-mean((phi.est-logit.phi)^2)
MSE.NS1.lam1<-mean((lam1.est.ll-log.lam1)^2)
MSE.NS1.lam2<-mean((lam2.est.ll-log.lam2)^2)
MSE.NS1.phi<-mean((phi.est.ll-logit.phi)^2)
NS1.MSE<-c(MSE.NS1.lam1,MSE.NS1.lam2,MSE.NS1.phi)
NWratio.MSE<-1/c(MSE.NS1.lam1/MSE.WS0.lam1,MSE.WS0.lam2,MSE.WS0.phi)
NSratio.MSE<-1/c(MSE.NS1.lam1/MSE.S0.lam1,MSE.NS1.lam2/MSE.S0.lam2,MSE.NS1.phi/MSE.S0.phi)
round(NWratio.MSE,3)
round(NSratio.MSE,3)

```

